\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{CJKutf8} % For Japanese support


% -------------------------------------
% 1) Bring in the 'titlesec' package:
% -------------------------------------
\usepackage{titlesec}

% -------------------------------------
% 2) Define custom formatting for \section:
%    - [display] puts the section title on its own line.
%    - \titlerule draws a horizontal line right after the title.
% -------------------------------------
\titleformat{\section}[display]
  {\normalfont\Large\bfseries}  % Format for the section title text
  {}
  {0pt}
  {}
  [\vspace{1mm}\titlerule]      % Horizontal line after the section

% -------------------------------------
% 3) If you do NOT want section numbers at all,
%    just hide them using \setcounter{secnumdepth}{0}.
% -------------------------------------
\setcounter{secnumdepth}{0}

\setstretch{1.1} % Adjust line spacing if desired

\begin{document}

\thispagestyle{empty}

%------------------------------------------
% Title and Contact Information
%------------------------------------------
\begin{center}
    {\Large \textbf{Jun Goto}} \\
    \vspace{2mm}
    \textbf{Associate Professor} \\
    National Graduate Institute for Policy Studies (GRIPS) \\
    7-22-1 Roppongi, Minato-ku, Tokyo, Japan 106-8677 \\
    \vspace{2mm}
    \texttt{Email:} \href{mailto:ju-goto@grips.ac.jp}{ju-goto@grips.ac.jp} \\
    \texttt{Personal Website:} \href{https://jungoto01.github.io/}{https://jungoto01.github.io/} \\
    \vspace{2mm}
    \today
\end{center}

\vspace{0.5cm}

%------------------------------------------
% Research Fields
%------------------------------------------
\section*{Research Fields}
\begin{itemize}
    \item Development Economics
    \item Political Economy
    \item Natural Language Processing (NLP)
\end{itemize}

%------------------------------------------
% Academic Employment
%------------------------------------------
\section*{Academic Employment}
\begin{itemize}
    \item \textbf{April 2014 -- March 2017}: Assistant Professor, Hitotsubashi University
    \item \textbf{April 2017 -- July 2017}: Research Fellow, The Tokyo Foundation
    \item \textbf{July 2017 -- December 2017}: Research Fellow, National Graduate Institute for Policy Studies (GRIPS)
    \item \textbf{January 2018 -- September 2022}: Associate Professor, Kobe University
    \item \textbf{October 2022 -- September 2025}: Assistant Professor, National Graduate Institute for Policy Studies (GRIPS)
    \item \textbf{October 2025 -- Present}: Associate Professor, National Graduate Institute for Policy Studies (GRIPS)
\end{itemize}

%------------------------------------------
% Visiting Positions
%------------------------------------------
\section*{Visiting Positions}
\begin{itemize}
    \item \textbf{January 2015 -- March 2015}: Visiting Scholar, Oxford University
    \item \textbf{August 2016 -- March 2017}: Visiting Scholar, London School of Economics
\end{itemize}

%------------------------------------------
% Education
%------------------------------------------
\section*{Education}
\begin{itemize}
    \item \textbf{Ph.D. in Agricultural Science, University of Tokyo}, March 2014 \\
    \textit{Dean's Award for Academic Excellence}

    \item \textbf{M.A. in Agricultural Science, University of Tokyo}, March 2009 \\
    \textit{Dean's Award for Academic Excellence}

    \item \textbf{B.A. in Economics, Chuo University}, March 2007 \\
    \textit{4th JBIC Thesis Contest: Best Thesis}
\end{itemize}

%------------------------------------------
% Published or Forthcoming Papers
%------------------------------------------
\section*{Published or Forthcoming Papers}
\begin{enumerate}
    \item \textbf{Goto, Jun}. 
    ``Career Incentives and Judicial Independence: Evidence from the Indian Lower Judiciary.'' Accepted, \textbf{\textit{Journal of Development Economics}}.

    \item Mori, Yuko, Rajasekhar D., Manjula R., Takashi Kurosaki, and \textbf{Jun Goto} (2025). 
    ``Who Becomes a Politician in a Gender Quota System? Evidence from India.'' 
    \textbf{\textit{World Development}}, Vol. 188.

    \item \textbf{Goto, Jun} and Takahiro Matsui (2025). 
    ``Counterproductive Punishment in Closed Communities: Experimental Evidence from Japanese Fishery.'' 
    \textbf{\textit{Marine Policy}}, Vol. 177.

    \item Mori, Yuko, Rajasekhar D., Manjula R., Takashi Kurosaki, and \textbf{Jun Goto} (2024). 
    ``Do Women Council Members Allocate More Public Goods? Evidence from Rural India.'' 
    \textbf{\textit{Economic Development and Cultural Change}} 73(1): 451--486.

    \item \textbf{Goto, Jun}, Takashi Kurosaki, and Yuko Mori (2022). 
    ``Distance to News: How Social Media Information Affects Bribe-Giving in India.'' 
    \textbf{\textit{Japanese Economic Review}} 73: 179--209. \\
    \textit{(Selected for the 2022 JER Best Article Award)}

    \item \textbf{Goto, Jun} (2013). 
    ``The Impacts of Self-Help Group Programs: Experimental and Survey Evidence from South India.'' 
    \textbf{\textit{Economics Bulletin}} 33(4): 2874--2889.
\end{enumerate}

%------------------------------------------
% Working Papers
%------------------------------------------
\section*{Working Papers}
\begin{enumerate}
    \item Takahashi, Kazushi, Abu S. Shonchoy, Takeshi Aida, \textbf{Jun Goto}, Yu Ri Kim, Hisaki Kono, and Takashi Kurosaki. 
    ``Saving for the Lean Season and Seasonal Poverty Dynamics: Evidence from a Randomized Experiment and High-Frequency Data.'' \\
    \textit{(ADB--IEA Innovative Policy Award 2023, Honorable Mention)}

    \item \textbf{Goto, Jun} and Tsuyoshi Tsuru. 
    ``Social Approval Seeking and Misperceived Legitimization: The Roots of Toxicity in Online Communities.'' 
    Submitted to \textit{Journal of Political Economy}.

    \item \textbf{Goto, Jun}, Takashi Kurosaki, and Yuko Mori. 
    ``Vocal Minorities and Polarization: How Extreme Views Erode Pro-Social Consensus on Social Media.'' \\
    \textit{(First Hayami Award at the 3rd Japanese Association for Development Economics (JADE) Conference)}

    \item \textbf{Goto, Jun} and Kai Kajitani. 
    ``The Long-Run Effects of Patriotic Education During Political Repression: Evidence from the Cultural Revolution in China.''.

    \item \textbf{Goto, Jun}, Yasuyuki Sawada, and Takeshi Aida. 
    ``Conformity of Social Preferences Through Regular Interactions: Field Experiments in the Workplace.'' 
    (February 22, 2023). Available at SSRN: \href{http://dx.doi.org/10.2139/ssrn.4366651}{http://dx.doi.org/10.2139/ssrn.4366651}

    \item Aoki, Miri, and \textbf{Jun Goto}, "Building a National Identity Rooted in Democratic Values Among Political Leaders: Evidence from the Pro-democracy Movement in Taiwan."
\end{enumerate}

%------------------------------------------
% Work in Progress
%------------------------------------------
\section*{Work in Progress}
\begin{itemize}
    \item ``Politician's Term Length in Nation Building: A Historical Natural Experiment in India'' 
    (with Tomoko Matsumoto, Shunsuke Tsuda, Junichi Yamasaki)

    \item ``Social Media, Discrimination, and Politics: Online Field Experiments in India''

    \item ``On the Origins and Persistence of Parochial Altruism: A Tenure Institution and Intergroup Conflicts in Colonial India''
\end{itemize}

%------------------------------------------
% Published Papers in Japanese
%------------------------------------------
\section*{Published Papers in Japanese}
\begin{enumerate}
    \item \textbf{Goto, Jun}, Ishizaki Hironori, Kurosaki Takashi, Sawada Yasuyuki, and Tsuda Shunsuke, (2018). ``Entrepreneurship,Informality,and Preference Heterogeneity within Small and Micro-Businesses in India'' \textit{The Economic Review}, 69(3) 242-275. 

    \item \textbf{Goto, Jun} and Yoichi Izumida (2009). 
    ``Efficiency and Welfare Impacts of Landholdings in Vietnam: Evidence from a Field Survey in the Red River and Mekong Deltas.'' 
    \textit{Japanese Journal of Farm Management} 47(2).

    \item \textbf{Goto, Jun}, Saori Iwase, Nao Takayama, and Yoichi Izumida (2008). 
    ``Changes in Landholdings in the Mekong Delta: Evidence from Household Survey in An Giang Province.'' 
    \textit{Journal of Rural Economics (Special Issue)}: 361--367.

    \item Takayama, Nao, Saori Iwase, \textbf{Jun Goto}, and Yoichi Izumida (2008). 
    ``Changes in Cost Structure of Rice Production in the Red River Delta: Evidence from Household Survey in Ninh Binh Province.'' 
    \textit{Journal of Rural Economics (Special Issue)}: 356--360.

    \item Iwase, Saori, Nao Takayama, \textbf{Jun Goto}, and Yoichi Izumida (2008). 
    ``The Role of Finance in Rural Household Economy in the Red River Delta.'' 
    \textit{Journal of Rural Economics (Special Issue)}: 348--355.

    \item \textbf{Goto, Jun} (2007). 
    ``The Functioning of Group Lending and the Role of Community in Microfinance: Evidence from Kerala, India.'' 
    \textit{The 4th JBIC Thesis Contest: Best Thesis, Journal of JBIC Institute} 35: 211--225.
\end{enumerate}

%------------------------------------------
% Books
%------------------------------------------
\section*{Books}
\begin{itemize}
    \item \textbf{Goto, Jun}, (2024) ''Comments: Implementing Empirical Economics into Policymaking'' in \textit{Next-Generation of Empirical Research in Economics}. eds. Keijiro. Otsuka., Takashi. Kurosaki., Yasuyuki. Sawada., and Tetsushi. Sonobe. Springer. 
\end{itemize}

%------------------------------------------
% Presentation
%------------------------------------------
\section*{Recent Presentations}
\begin{itemize}
    \item \textbf{2025}: JADE annual conference, J-TREE workshop, Hitotsubashi University, KDI school, The Tokyo Conference on Institutions, Law, and Development (scheduled)
    \item \textbf{2024}: Musashi University, Kyoto University, Korean Development Institute, KDI-DIME (World Bank) Joint Conference, Tokyo Labor Economics Workshop, JADE-JTREE joint Conference, SIOE conference
    \item \textbf{2023}: Kansai Labor Economics Workshop, Annual Midwest Political Science Association Conference, HSI 2023, SWET, Monash-Warwick-Zurich Text-As-Data Workshop, Tsukuba University, Sophia University
    \item \textbf{2022}: Royal Economic Society Annual Conference, SWET, The Hong Kong University of Science and Technology, ASAE
\end{itemize}

%------------------------------------------
% Awards
%------------------------------------------
\section*{Awards}
\begin{itemize}
    \item \textbf{``Saving for the Lean Season and Seasonal Poverty Dynamics''} (with Kazushi Takahashi, Abu S. Shonchoy, Takeshi Aida, Yu Ri Kim, Hisaki Kono, and Takashi Kurosaki) \\
    ADB--IEA Innovative Policy Award 2023, Honorable Mention

    \item \textbf{``Distance to News: How Social Media Information Affects Bribe-Giving in India''} (with Takashi Kurosaki, Yuko Mori), 
    \textit{Japanese Economic Review (2022)}, 73:179--209 \\
    Selected for the 2022 JER Best Article Award

    \item First Hayami Award at the 3rd Japanese Association for Development Economics (JADE) Conference, April 2021

    \item Dean's Award for Academic Excellence, Dept. of Agricultural and Resource Economics, University of Tokyo, March 2014

    \item The 5th Annual Meeting Association of Behavioral Economics and Finance, Incentive Award, January 2012

    \item Award for Young Economists in International Association for Agricultural Economists (IAAE) Japanese Branch, Beijing, October 2009

    \item Dean's Award for Academic Excellence, Dept. of Agricultural and Resource Economics, University of Tokyo, March 2009

    \item 4th Japan Bank for International Cooperation (JBIC) Thesis Contest: Best Thesis, September 2007
\end{itemize}

%------------------------------------------
% Teaching
%------------------------------------------
\section*{Teaching}

\begin{itemize}
\item \textbf{Hitotsubashi University}
\begin{itemize}
    \item Development Economics (Graduate)
\end{itemize}

\item \textbf{Kobe University}
\begin{itemize}
    \item Development Economics (Undergraduate)
    \item Development Economics (Graduate)
    \item International Economics (Undergraduate)
    \item Introduction to Empirical Economics (Undergraduate)
\end{itemize}

\item \textbf{GRIPS}
\begin{itemize}
    \item Data Science for Public Policy (Graduate)
    \item Advanced Econometrics IV (Ph.D): The Frontiers of Text Analysis in Economics
    \item Applied Econometrics (Japanese, Graduate)
    \item Tutorial Session (Ph.D): Web Scraping, Text Analysis, and Research Management Practices Using GitHub
\end{itemize}
\end{itemize}
%------------------------------------------
% Grants
%------------------------------------------
\section*{Grants}
\begin{itemize}
    \item \textbf{The State’s Hand and Media Self-Censorship: An Empirical Investigation Using Machine-Learning Approaches},\\
    Grant-in-Aid for Scientific Research (C), 2025--2029 \\ (Principal Investigator)

    \item \textbf{Factors Promoting \& Restraining Discrimination in Online Communities: An Empirical Analysis of \textit{Yahoo! Chiebukuro}},\\
    Grant-in-Aid for Scientific Research (C), 2024--2026 \\ (Co-Investigator)

    \item \textbf{De-radicalisation \& Social Reintegration of Former Combatants in Islamic Conflicts: Evidence from Somalia},\\
    Nomura Foundation Research Grant, 2024--2026 \\ (Principal Investigator)

    \item \textbf{Cooperative Behavior, Economic Incentives, and Social Reputation: Natural Experiments in a Japanese Q\&A Site}, 
    Grant-in-Aid for Scientific Research (C), 2020--2022 \\ (Co-Investigator)

    \item \textbf{Analysis of the Effects of Information Transmission, Adjustment of interests, and Political Participation under Democracy}, 
    Grant-in-Aid for Scientific Research (B), 2019--2022 \\ (Co-Investigator)

    \item \textbf{Incentives for Politicians in Nation-Building: A Text Analysis with Assembly Records}, 
    Grant-in-Aid for Scientific Research (C), 2019--2024 \\ (Principal Investigator)

    \item \textbf{Seasonal vulnerability of the ultra-poor and its remedy: An approach through a high frequent survey and randomized experiment}, 
    Grant-in-Aid for Scientific Research (B), 2017--2021 \\ (Co-Investigator)

    \item \textbf{Study of Food Consumption Behavior: An Experimental Economics Approach}, 
    Grant-in-Aid for Challenging Exploratory Research, 2015--2017 \\ (Principal Investigator)

    \item \textbf{The Behavioral Theory for Informal Institutions: Experimental Evidence from Developing Countries}, 
    Grant-in-Aid for Young Scientists (B), 2015--2016 \\ (Principal Investigator)

    \item DC1 Research Fellow, Japan Society for the Promotion of Science (JSPS), 2009--2012
\end{itemize}


%------------------------------------------
% Skills Section
%------------------------------------------
\section*{Skills}

\begin{itemize}
  % 1) Languages
  \item \textbf{Languages}: Japanese (native), English (fluent)
  % 2) Coding
  \item \textbf{Coding}: Java, Stata, Python, R, SQL, XML/XSL, \LaTeX,\dots
  % 3) Databases
  \item \textbf{Databases}: MySQL, SQLite
  % 4) Web Dev
  \item \textbf{Web Dev}: HTML, CSS, JavaScript
\end{itemize}

%------------------------------------------
% Memberships
%------------------------------------------
\section*{Memberships}
\begin{itemize}
    \item American Economic Association
    \item The Econometric Society
    \item Japanese Association for Development Economics
\end{itemize}


\end{document}
